---
title: "Simulating VAR-type Minnesota BVHAR"
author: "Young Geun Kim"
date: "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  github_document:
    toc: true
knit:
  (function(inputFile, encoding) {
    rmarkdown::render(
      input = inputFile,
      output_dir = "../docs", 
      encoding = encoding
    )
  })
---

```{r simdata}
sim_data <- "../data/processed/bvharsim_dgp_s.rds"
```

```{r cacheset, include=FALSE, cache=TRUE, cache.extra = tools::md5sum(sim_data)}
knitr::opts_chunk$set(cache.rebuild = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  out.width = "70%",
  fig.path = "../output/figs/DGP-3-",
  fig.align = "center",
  fig.width = 6,
  fig.asp = .618
)
knitr::knit_hooks$set(
  document = function(x) {
    sub("\\usepackage[]{color}", "\\usepackage{xcolor}", x, fixed = TRUE)
  }
)
options(digits = 3)
# options(scipen = -2) # scientific notation digits
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)
is_html <- knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == "latex"
kable_format <- ifelse(!is_html, "latex", "html")
kable_format <- ifelse(length(kable_format) == 0, "html", kable_format) # for excecutable
```

```{r pkgs, message=FALSE}
# tidyverse----------------------------
library(tidyverse)
# BVHAR custom package-----------------
library(bvhar)
# Set the number of processor cores----
cl <- parallel::makeCluster(8, type = "FORK")
# set seed for reproducible result-----
set.seed(1)
```

```{r fns, message=FALSE}
# result table-------------------------
source("report-fns.R")
# hyperparameter setting table---------
source("param-fns.R")
# Simulation---------------------------
dgp <- readRDS(sim_data)
```

# BVHAR Coefficient

## VAR-type Minnesota prior

```{r smalltruesetting, comment=NULL, echo=FALSE}
bvhar_small_spec <- dgp$small_spec
```

```{r medtruesetting, comment=NULL, echo=FALSE}
bvhar_medium_spec <- dgp$medium_spec
```

```{r largetruesetting, comment=NULL, echo=FALSE}
bvhar_large_spec <- dgp$large_spec
```

```{r simulcase}
n_small <- length(bvhar_small_spec$sigma)
n_medium <- length(bvhar_medium_spec$sigma)
n_large <- length(bvhar_large_spec$sigma)
```

## VAR(5)

### SMALL

```{r smalldata}
y_small_train <- dgp$y_small_train
y_small_test <- dgp$y_small_test
```

```{r smallplot}
y_small_train %>% 
  mutate(train = TRUE) %>% 
  bind_rows(y_small_test %>% mutate(train = FALSE)) %>% 
  mutate(id = 1:n()) %>% 
  pivot_longer(-c(id, train), names_to = "asset", values_to = "value") %>% 
  ggplot(aes(x = id, y = value)) +
  annotate(
    geom = "rect",
    xmin = nrow(y_small_train),
    xmax = nrow(y_small_train) + nrow(y_small_test),
    ymin = -Inf,
    ymax = Inf,
    alpha = .7,
    fill = "grey" # test set
  ) +
  geom_path() +
  facet_grid(asset ~ ., scales = "free_y") +
  scale_x_continuous(
    breaks = c(nrow(y_small_train), nrow(y_small_train) + nrow(y_small_test))
  ) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = NA)) +
  labs(
    x = element_blank(),
    y = element_blank()
  )
```

### MEDIUM

```{r meddata}
y_medium_train <- dgp$y_medium_train
y_medium_test <- dgp$y_medium_test
```

```{r medplot}
y_medium_train %>% 
  mutate(train = TRUE) %>% 
  bind_rows(y_medium_test %>% mutate(train = FALSE)) %>% 
  mutate(id = 1:n()) %>% 
  pivot_longer(-c(id, train), names_to = "asset", values_to = "value") %>% 
  ggplot(aes(x = id, y = value)) +
  annotate(
    geom = "rect",
    xmin = nrow(y_medium_train),
    xmax = nrow(y_medium_train) + nrow(y_medium_test),
    ymin = -Inf,
    ymax = Inf,
    alpha = .7,
    fill = "grey" # test set
  ) +
  geom_path() +
  facet_grid(asset ~ ., scales = "free_y") +
  scale_x_continuous(
    breaks = c(nrow(y_medium_train), nrow(y_medium_train) + nrow(y_medium_test))
  ) +
  theme_minimal() +
  theme(
    strip.text.y = element_text(size = 5), 
    panel.border = element_rect(fill = NA)
  ) +
  labs(
    x = element_blank(),
    y = element_blank()
  )
```

### LARGE

```{r largedata}
y_large_train <- dgp$y_large_train
y_large_test <- dgp$y_large_test
```

```{r largeplot}
y_large_train %>% 
  mutate(train = TRUE) %>% 
  bind_rows(y_large_test %>% mutate(train = FALSE)) %>% 
  mutate(id = 1:n()) %>% 
  pivot_longer(-c(id, train), names_to = "asset", values_to = "value") %>% 
  ggplot(aes(x = id, y = value)) +
  annotate(
    geom = "rect",
    xmin = nrow(y_large_train),
    xmax = nrow(y_large_train) + nrow(y_large_test),
    ymin = -Inf,
    ymax = Inf,
    alpha = .7,
    fill = "grey" # test set
  ) +
  geom_path(size = .3) +
  facet_grid(asset ~ ., scales = "free_y") +
  scale_x_continuous(
    breaks = c(nrow(y_large_train), nrow(y_large_train) + nrow(y_large_test))
  ) +
  theme_minimal() +
  theme(
    strip.text.y = element_text(size = 5), 
    panel.border = element_rect(fill = NA),
    axis.text.y = element_text(size = 3)
  ) +
  labs(
    x = element_blank(),
    y = element_blank()
  )
```


# Modeling

## VAR

```{r varorder}
(var_lag <- 5)
```

```{r varfit}
fit_var_small <- var_lm(y_small_train, var_lag, include_mean = FALSE)
fit_var_medium <- var_lm(y_medium_train, var_lag, include_mean = FALSE)
fit_var_large <- var_lm(y_large_train, var_lag, include_mean = FALSE)
```

## VHAR

```{r vharfit}
fit_vhar_small <- vhar_lm(y_small_train, include_mean = FALSE)
fit_vhar_medium <- vhar_lm(y_medium_train, include_mean = FALSE)
fit_vhar_large <- vhar_lm(y_large_train, include_mean = FALSE)
```

## BVAR

```{r bvarorder}
(bvar_lag <- 5)
```

```{r bvarsetting}
bvar_small_spec <- set_bvar(
  sigma = bvhar_small_spec$sigma,
  lambda = bvhar_small_spec$lambda,
  delta = bvhar_small_spec$delta
)
#----------------------------
bvar_medium_spec <- set_bvar(
  sigma = bvhar_medium_spec$sigma,
  lambda = bvhar_medium_spec$lambda,
  delta = bvhar_medium_spec$delta
)
#----------------------------
bvar_large_spec <- set_bvar(
  sigma = bvhar_large_spec$sigma,
  lambda = bvhar_large_spec$lambda,
  delta = bvhar_large_spec$delta
)
```

```{r smallbvaroptim, cache = 1}
(bvar_small_optim <- choose_bvar(
  bvar_small_spec, 
  lower = c(
    rep(.5, n_small), # sigma
    1e-4, # lambda
    rep(0, n_small) # delta
  ), 
  upper = c(
    rep(5, n_small), # sigma
    Inf, # lambda
    rep(1, n_small) # delta
  ), 
  y = y_small_train, 
  p = bvar_lag, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r medbvaroptim, cache = 1}
(bvar_medium_optim <- choose_bvar(
  bvar_medium_spec, 
  lower = c(
    rep(.5, n_medium), # sigma
    1e-4, # lambda
    rep(0, n_medium) # delta
  ), 
  upper = c(
    rep(5, n_medium), # sigma
    Inf, # lambda
    rep(1, n_medium) # delta
  ), 
  y = y_medium_train, 
  p = bvar_lag, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r largebvaroptim, cache = 1}
(bvar_large_optim <- choose_bvar(
  bvar_large_spec, 
  lower = c(
    rep(.5, n_large), # sigma
    1e-4, # lambda
    rep(0, n_large) # delta
  ), 
  upper = c(
    rep(5, n_large), # sigma
    Inf, # lambda
    rep(1, n_large) # delta
  ), 
  y = y_large_train, 
  p = bvar_lag, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r bvarfit}
fit_small_bvar <- bvar_small_optim$fit
fit_medium_bvar <- bvar_medium_optim$fit
fit_large_bvar <- bvar_large_optim$fit
```

## BVHAR-VAR

```{r smallbvharoptim, cache = 1}
(bvhar_var_small_optim <- choose_bvhar(
  bvhar_small_spec, 
  lower = c(
    rep(.5, n_small), # sigma
    1e-4, # lambda
    rep(0, n_small) # delta
  ), 
  upper = c(
    rep(5, n_small), # sigma
    Inf, # lambda
    rep(1, n_small) # delta
  ), 
  y = y_small_train, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r medbvharoptim, cache = 1}
(bvhar_var_medium_optim <- choose_bvhar(
  bvhar_medium_spec, 
  lower = c(
    rep(.5, n_medium), # sigma
    1e-4, # lambda
    rep(0, n_medium) # delta
  ), 
  upper = c(
    rep(5, n_medium), # sigma
    Inf, # lambda
    rep(1, n_medium) # delta
  ), 
  y = y_medium_train, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r largebvharoptim, cache = 1}
(bvhar_var_large_optim <- choose_bvhar(
  bvhar_large_spec, 
  lower = c(
    rep(.5, n_large), # sigma
    1e-4, # lambda
    rep(0, n_large) # delta
  ), 
  upper = c(
    rep(5, n_large), # sigma
    Inf, # lambda
    rep(1, n_large) # delta
  ), 
  y = y_large_train, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r bvharvarfit}
fit_bvhar_small_var <- bvhar_var_small_optim$fit
fit_bvhar_medium_var <- bvhar_var_medium_optim$fit
fit_bvhar_large_var <- bvhar_var_large_optim$fit
```

## BVHAR-VHAR

```{r bvharvharsetting}
bvhar_vhar_small_spec <- set_weight_bvhar(
  sigma = bvhar_small_spec$sigma,
  lambda = bvhar_small_spec$lambda,
  daily = bvhar_small_spec$delta,
  weekly = bvhar_small_spec$delta,
  monthly = bvhar_small_spec$delta
)
#-----------------------------------------
bvhar_vhar_medium_spec <- set_weight_bvhar(
  sigma = bvhar_medium_spec$sigma,
  lambda = bvhar_medium_spec$lambda,
  daily = bvhar_medium_spec$delta,
  weekly = bvhar_medium_spec$delta,
  monthly = bvhar_medium_spec$delta
)
#-----------------------------------------
bvhar_vhar_large_spec <- set_weight_bvhar(
  sigma = bvhar_large_spec$sigma,
  lambda = bvhar_large_spec$lambda,
  daily = bvhar_large_spec$delta,
  weekly = bvhar_large_spec$delta,
  monthly = bvhar_large_spec$delta
)
```

```{r smallbvharvharoptim, cache = 1}
(bvhar_vhar_small_optim <- choose_bvhar(
  bvhar_vhar_small_spec, 
  lower = c(
    rep(.5, n_small), # sigma
    1e-4, # lambda
    rep(0, n_small), # daily
    rep(0, n_small), # weekly
    rep(0, n_small) # monthly
  ), 
  upper = c(
    rep(5, n_small), # sigma
    Inf, # lambda
    rep(1, n_small), # daily
    rep(1, n_small), # weekly
    rep(1, n_small) # monthly
  ), 
  y = y_small_train, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r medbvharvharoptim, cache = 1}
(bvhar_vhar_medium_optim <- choose_bvhar(
  bvhar_vhar_medium_spec, 
  lower = c(
    rep(.5, n_medium), # sigma
    1e-4, # lambda
    rep(0, n_medium), # daily
    rep(0, n_medium), # weekly
    rep(0, n_medium) # monthly
  ), 
  upper = c(
    rep(5, n_medium), # sigma
    Inf, # lambda
    rep(1, n_medium), # daily
    rep(1, n_medium), # weekly
    rep(1, n_medium) # monthly
  ), 
  y = y_medium_train, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r largebvharvharoptim, cache = 1}
(bvhar_vhar_large_optim <- choose_bvhar(
  bvhar_vhar_large_spec, 
  lower = c(
    rep(.5, n_large), # sigma
    1e-4, # lambda
    rep(0, n_large), # daily
    rep(0, n_large), # weekly
    rep(0, n_large) # monthly
  ), 
  upper = c(
    rep(5, n_large), # sigma
    Inf, # lambda
    rep(1, n_large), # daily
    rep(1, n_large), # weekly
    rep(1, n_large) # monthly
  ), 
  y = y_large_train, 
  include_mean = FALSE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r bvharvharfit}
fit_bvhar_small_vhar <- bvhar_vhar_small_optim$fit
fit_bvhar_medium_vhar <- bvhar_vhar_medium_optim$fit
fit_bvhar_large_vhar <- bvhar_vhar_large_optim$fit
```

```{r stopcl}
parallel::stopCluster(cl)
```


## Hyperparameters

```{r reportemp, comment=NULL, echo=FALSE}
spec_optim_list <- list(
  small = list(
    bvar_small_optim$spec,
    bvhar_var_small_optim$spec,
    bvhar_vhar_small_optim$spec
  ),
  medium = list(
    bvar_medium_optim$spec,
    bvhar_var_medium_optim$spec,
    bvhar_vhar_medium_optim$spec
  ),
  large = list(
    bvar_large_optim$spec,
    bvhar_var_large_optim$spec,
    bvhar_vhar_large_optim$spec
  )
)
# report-------------------
report_hyperparam(spec_optim_list, report_true = FALSE, caption = "Empirical Bayes Results for DGP3.", label = "empdgp3") %>% 
  writeLines()
```

# Errors

## Rolling Windows

```{r listroll, cache = 1}
# model lists-------------------------
mod_small_list <- list(
  fit_var_small,
  fit_vhar_small,
  fit_small_bvar,
  fit_bvhar_small_var,
  fit_bvhar_small_vhar
)
mod_medium_list <- list(
  fit_var_medium,
  fit_vhar_medium,
  fit_medium_bvar,
  fit_bvhar_medium_var,
  fit_bvhar_medium_vhar
)
mod_large_list <- list(
  fit_var_large,
  fit_vhar_large,
  fit_large_bvar,
  fit_bvhar_large_var,
  fit_bvhar_large_vhar
)
# SMALL-------------------------------
cv_small_list <- 
  parallel::mclapply(
    c(1, 5, 10, 20),
    function(h) {
      mod_small_list %>% 
        lapply(
          function(mod) {
            forecast_roll(mod, h, y_small_test)
          }
        )
    },
    mc.cores = 8
  )
# MEDIUM------------------------------
cv_medium_list <- 
  parallel::mclapply(
    c(1, 5, 10, 20),
    function(h) {
      mod_medium_list %>% 
        lapply(
          function(mod) {
            forecast_roll(mod, h, y_medium_test)
          }
        )
    },
    mc.cores = 8
  )
# LARGE-------------------------------
cv_large_list <- 
  parallel::mclapply(
    c(1, 5, 10, 20),
    function(h) {
      mod_large_list %>% 
        lapply(
          function(mod) {
            forecast_roll(mod, h, y_large_test)
          }
        )
    },
    mc.cores = 8
  )
```


## Relative Error

Set VAR as the benchmark model.

```{r simaveresult, comment=NULL, echo=FALSE}
get_rmafetex_tr(
  list(cv_small_list, cv_medium_list, cv_large_list), 
  y_list = list(y_small_test, y_medium_test, y_large_test), 
  ahead_list = c("$h = 1$", "$h = 5$", "$h = 10$", "$h = 20$"),
  benchmark_id = 1,
  caption = "Out-of-sample forecasting performance measures for DGP3 with VAR(5) model as benchmark.", 
  label = "dgp3result",
  header_angle = 0
) %>% 
  writeLines()
```


## Piecewise Errors

### SMALL

Plots

```{r smallcvonefig, echo=FALSE}
cv_small_list[[1]] %>% 
  gg_loss(
    y_small_test, 
    mean_line = TRUE, 
    line_param = list(size = .3), 
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

```{r smallcvfivefig, echo=FALSE}
cv_small_list[[2]] %>% 
  gg_loss(
    y_small_test, 
    mean_line = TRUE, 
    line_param = list(size = .3), 
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

```{r smallcvtwentyfig, echo=FALSE}
cv_small_list[[3]] %>% 
  gg_loss(
    y_small_test, 
    mean_line = TRUE, 
    line_param = list(size = .3), 
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

Tables

1-step:

```{r smallcvconetab, comment=NULL, echo=FALSE}
cv_small_list[[1]] %>% 
  get_losstex(y_small_test, "SMALL Simulation - 1-step ahead Rolling Window Forecasting Loss", label = "smallone") %>% 
  writeLines()
```

5-step:

```{r smallcvfivetab, comment=NULL, echo=FALSE}
cv_small_list[[2]] %>% 
  get_losstex(y_small_test, "SMALL Simulation - 5-step ahead Rolling Window Forecasting Loss", label = "smallfive") %>% 
  writeLines()
```

20-step:

```{r smallcvtwentytab, comment=NULL, echo=FALSE}
cv_small_list[[3]] %>% 
  get_losstex(y_small_test, "SMALL Simulation - 20-step ahead Rolling Window Forecasting Loss", label = "smalltwenty") %>% 
  writeLines()
```

### MEDIUM

Plots

```{r medcvonefig}
cv_medium_list[[1]] %>% 
  gg_loss(
    y_medium_test, 
    mean_line = TRUE, 
    line_param = list(size = .3), 
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

```{r medcvfivefig}
cv_medium_list[[2]] %>% 
  gg_loss(
    y_medium_test, 
    mean_line = TRUE, 
    line_param = list(size = .3), 
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

```{r medcvtwentyfig}
cv_medium_list[[3]] %>% 
  gg_loss(
    y_medium_test, 
    mean_line = TRUE, 
    line_param = list(size = .3), 
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

Tables

1-step:

```{r medcvonetab, comment=NULL, echo=FALSE}
cv_medium_list[[1]] %>% 
  get_losstex(y_medium_test, "MEDIUM Simulation - 1-step ahead Rolling Window Forecasting Loss", label = "medone") %>% 
  writeLines()
```

5-step:

```{r medcvfivetab, comment=NULL, echo=FALSE}
cv_medium_list[[2]] %>% 
  get_losstex(y_medium_test, "MEDIUM Simulation - 5-step ahead Rolling Window Forecasting Loss", label = "medfive") %>% 
  writeLines()
```

20-step:

```{r medcvtwentytab, comment=NULL, echo=FALSE}
cv_medium_list[[3]] %>% 
  get_losstex(y_medium_test, "MEDIUM Simulation - 20-step ahead Rolling Window Forecasting Loss", label = "medtwenty") %>% 
  writeLines()
```

### LARGE

Plots

```{r largecvonefig}
cv_large_list[[1]] %>% 
  gg_loss(
    y_large_test, 
    mean_line = TRUE, 
    line_param = list(size = .3),
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

```{r largecvfivefig}
cv_large_list[[2]] %>% 
  gg_loss(
    y_large_test, 
    mean_line = TRUE, 
    line_param = list(size = .3),
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

```{r largecvtwentyfig}
cv_large_list[[3]] %>% 
  gg_loss(
    y_large_test, 
    mean_line = TRUE, 
    line_param = list(size = .3),
    mean_param = list(alpha = .5, size = .3), 
    viridis = TRUE, 
    show.legend = FALSE
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = -30, vjust = -1),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 7),
    legend.key.size = unit(.3, "cm")
  )
```

Tables

1-step:

```{r largecvonetab, comment=NULL, echo=FALSE}
cv_large_list[[1]] %>% 
  get_losstex(y_large_test, "LARGE Simulation - 1-step ahead Rolling Window Forecasting Loss", label = "largeone") %>% 
  writeLines()
```

5-step:

```{r largecvfivetab, comment=NULL, echo=FALSE}
cv_large_list[[2]] %>% 
  get_losstex(y_large_test, "LARGE Simulation - 5-step ahead Rolling Window Forecasting Loss", label = "largefive") %>% 
  writeLines()
```

20-step:

```{r largecvtwentytab, comment=NULL, echo=FALSE}
cv_large_list[[3]] %>% 
  get_losstex(y_large_test, "LARGE Simulation - 20-step ahead Rolling Window Forecasting Loss", label = "largetwenty") %>% 
  writeLines()
```

### Average

SMALL

1-step:

```{r smallcvonemeantab, comment=NULL, echo=FALSE}
cv_small_list[[1]] %>% 
  kable_lossmean(y_small_test, kable = TRUE, caption = "SMALL Simulation - 1-step ahead Rolling Window Forecasting Average Loss", label = "smallonemean") %>% 
  writeLines()
```

5-step:

```{r smallcvfivemeantab, comment=NULL, echo=FALSE}
cv_small_list[[2]] %>% 
  kable_lossmean(y_small_test, kable = TRUE, caption = "SMALL Simulation - 5-step ahead Rolling Window Forecasting Average Loss", label = "smallfivemean") %>% 
  writeLines()
```

20-step:

```{r smallcvtwentymeantab, comment=NULL, echo=FALSE}
cv_small_list[[3]] %>% 
  kable_lossmean(y_small_test, kable = TRUE, caption = "SMALL Simulation - 20-step ahead Rolling Window Forecasting Average Loss", label = "smalltwentyemean") %>% 
  writeLines()
```

MEDIUM

1-step:

```{r medcvonemeantab, comment=NULL, echo=FALSE}
cv_medium_list[[1]] %>% 
  kable_lossmean(y_medium_test, kable = TRUE, caption = "MEDIUM Simulation - 1-step ahead Rolling Window Forecasting Average Loss", label = "medonemean") %>% 
  writeLines()
```

5-step:

```{r medcvfivemeantab, comment=NULL, echo=FALSE}
cv_medium_list[[2]] %>% 
  kable_lossmean(y_medium_test, kable = TRUE, caption = "MEDIUM Simulation - 5-step ahead Rolling Window Forecasting Average Loss", label = "medfivemean") %>% 
  writeLines()
```

20-step:

```{r medcvtwentymeantab, comment=NULL, echo=FALSE}
cv_medium_list[[3]] %>% 
  kable_lossmean(y_medium_test, kable = TRUE, caption = "MEDIUM Simulation - 20-step ahead Rolling Window Forecasting Average Loss", label = "medtwentyemean") %>% 
  writeLines()
```

LARGE

1-step:

```{r largecvonemeantab, comment=NULL, echo=FALSE}
cv_large_list[[1]] %>% 
  kable_lossmean(y_large_test, kable = TRUE, caption = "LARGE Simulation - 1-step ahead Rolling Window Forecasting Average Loss", label = "largeonemean") %>% 
  writeLines()
```

5-step:

```{r largecvfivemeantab, comment=NULL, echo=FALSE}
cv_large_list[[2]] %>% 
  kable_lossmean(y_large_test, kable = TRUE, caption = "LARGE Simulation - 5-step ahead Rolling Window Forecasting Average Loss", label = "largefivemean") %>% 
  writeLines()
```

20-step:

```{r largecvtwentymeantab, comment=NULL, echo=FALSE}
cv_large_list[[3]] %>% 
  kable_lossmean(y_large_test, kable = TRUE, caption = "LARGE Simulation - 20-step ahead Rolling Window Forecasting Average Loss", label = "largetwentyemean") %>% 
  writeLines()
```


# Coefficients

```{r smallplotsave, eval=FALSE}
bayes_small_mod <- mod_small_list[3:5]
names(bayes_small_mod) <- sapply(bayes_small_mod, function(x) x$process)
small_vec <- names(y_small_train)
names(small_vec) <- names(y_small_train)
# draw---------------------
set.seed(1)
bayes_small_plot <- 
  bayes_small_mod %>% 
  lapply(
    function(mods) {
      lapply(
        small_vec,
        function(x) {
          autoplot(summary(mods), var_name = x) +
            theme_minimal()
        }
      )
    }
  )
# save---------------------
lapply(
  seq_along(bayes_small_plot),
  function(x) {
    process_name <- names(bayes_small_plot)[x] # one of the processes
    p_list <- bayes_small_plot[[process_name]]
    asset_name <- names(p_list) # character vector: asset_01, asset_02, ...
    lapply(
      asset_name,
      function(y) {
        file_name <- 
          paste0(
            "../output/dgp03-figs/small-coef/", 
            str_replace_all(process_name, pattern = "\\_", replacement = "\\-"), 
            "-", 
            str_remove_all(y, pattern = "\\_"),
            ".pdf"
          )
        ggsave(filename = file_name, plot = p_list[[y]])
      }
    )
  }
)
```

```{r medplotsave, eval=FALSE}
bayes_medium_mod <- mod_medium_list[3:5]
names(bayes_medium_mod) <- sapply(bayes_medium_mod, function(x) x$process)
medium_vec <- names(y_medium_train)
names(medium_vec) <- names(y_medium_train)
# draw---------------------
set.seed(1)
bayes_medium_plot <- 
  bayes_medium_mod %>% 
  lapply(
    function(mods) {
      lapply(
        medium_vec,
        function(x) {
          autoplot(summary(mods), var_name = x) +
            theme_minimal()
        }
      )
    }
  )
# save---------------------
lapply(
  seq_along(bayes_medium_plot),
  function(x) {
    process_name <- names(bayes_medium_plot)[x] # one of the processes
    p_list <- bayes_medium_plot[[process_name]]
    asset_name <- names(p_list) # character vector: asset_01, asset_02, ...
    lapply(
      asset_name,
      function(y) {
        file_name <- 
          paste0(
            "../output/dgp03-figs/med-coef/", 
            str_replace_all(process_name, pattern = "\\_", replacement = "\\-"), 
            "-", 
            str_remove_all(y, pattern = "\\_"),
            ".pdf"
          )
        ggsave(filename = file_name, plot = p_list[[y]])
      }
    )
  }
)
```

```{r largeplotsave, eval=FALSE}
bayes_large_mod <- mod_large_list[3:5]
names(bayes_large_mod) <- sapply(bayes_large_mod, function(x) x$process)
large_vec <- names(y_large_train)
names(large_vec) <- names(y_large_train)
# draw---------------------
set.seed(1)
bayes_large_plot <- 
  bayes_large_mod %>% 
  lapply(
    function(mods) {
      lapply(
        large_vec,
        function(x) {
          autoplot(summary(mods), var_name = x) +
            theme_minimal()
        }
      )
    }
  )
# save---------------------
lapply(
  seq_along(bayes_large_plot),
  function(x) {
    process_name <- names(bayes_large_plot)[x] # one of the processes
    p_list <- bayes_large_plot[[process_name]]
    asset_name <- names(p_list) # character vector: asset_01, asset_02, ...
    lapply(
      asset_name,
      function(y) {
        file_name <- 
          paste0(
            "../output/dgp03-figs/large-coef/", 
            str_replace_all(process_name, pattern = "\\_", replacement = "\\-"), 
            "-", 
            str_remove_all(y, pattern = "\\_"),
            ".pdf"
          )
        ggsave(filename = file_name, plot = p_list[[y]])
      }
    )
  }
)
```


